Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-09-12 paperDraft2.tex
finished assurnace section

@@

@@

>>>>

It should be noted that in this test planning process you would use the
posterior distribution of $\lambda_S$ from the final developmental testing
phase.  It is also common to incorporate a degradation factor to account for an
expected reduction in reliability from the developmental phase to the
operational phase.  In the Bayesian framework, this entails adding another
multiplicative parameter to the rate parameter with an appropriate prior.   A
10-30 percent reduction from the developmental phase to the operational phase is
common in many DoD applications.

@@

From here we are able to find combinations of failures allowed and test miles
required that satisfy both risk requirements.  The table below show the
resulting combinations for the JLTV data.

@@

It should be noted that if $\pi_0$, $\pi_1$, $\alpha$ and $\beta$ are set to
unrealisitc values there can be situations where no combinations of failures
allowed and test miles required will satisfy these probability statements.  In
this paper we have focused on test plans for single units, but this methodology
can be extended to find test plans that allow for a changing number of testing
units.  In this case you would find combinations of failures allowed and test
miles required and number of vehicles tested that satisfy the risk requirements.
More details and examples of this can be found in the assurance testing section
of Hamada et al. ~\cite{ref4}

\subsection{Discussion}
